---
title: "tidy_tuesday_3_submission_numbats"
author: "Mac"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../Output/")
```

# Load Libraries

```{r}
library(tidyverse)
library(here)
library(tidytuesdayR)
library(lubridate)
library(kableExtra)
library(maps)
library(mapdata)
library(mapproj)
library(ozmaps)
library(oz)
```

# Load Data

```{r}
#tuesdata <- tidytuesdayR::tt_load('2023-03-07')
#tuesdata <- tidytuesdayR::tt_load(2023, week = 10)

#numbats <- tuesdata$numbats

numbats <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-03-07/numbats.csv')
```

# Data Analysis

Questions that would be interesting to answer are:

Where do you find numbats in Australia?
Was the distribution more widespread historically? (You may need to exclude zoo reported observations.)
What time of day do numbat sightings occur?
Are they more frequent in the summer or winter?
Are numbats seen more on sunny and warm days than cloudy, wet, cold days?
Do sightings happen more on week days than weekends?

```{r}
head(numbats) %>%
  kbl() %>% # Make it a kable table
  kable_classic() %>%
  kable_styling(full_width = FALSE) # Disabling full width option
```

# Version of map made using mapdata

```{r Map of numbat sightings by subspecies}

world <- map_data("world")

ggplot()+
  geom_polygon(data = world, 
               aes(x = long, 
                   y = lat, 
                   group = group),
               color = "black", fill = "yellowgreen") +
  geom_point(data = numbats,
             aes(x = decimalLongitude,
                 y = decimalLatitude,
                 group = scientificName,
                 color = scientificName),
             alpha = 0.5) +
  coord_map(projection = "mercator",
            xlim = c(115, 180),
            ylim = c(-10, -40)) + # can set limits of longitude (xlim) and latitude (ylim?) to zoom in
  labs(title = "Locations of numbat sightings in Australia",
       x = "Longitude",
       y = "Latitude", 
       color = "Subspecies") +
  scale_colour_manual(values = c("lightseagreen",
                                 "violetred1"),
                      aesthetics = c("color",
                                     "fill")) +
  theme(panel.background = element_rect(fill = "lightblue"))
```

# Version of map made using ozmaps

```{r Second map of numbat sightings by subspecies}
ggplot(ozmap_data("states")) +
  geom_sf(fill = "yellowgreen") +
  geom_point(data = numbats,
             aes(x = decimalLongitude,
                 y = decimalLatitude,
                 group = scientificName,
                 color = scientificName),
             alpha = 0.5) +
  labs(title = "Locations of numbat sightings in Australia",
       x = "Longitude",
       y = "Latitude", 
       color = "Subspecies") +
  scale_colour_manual(values = c("lightseagreen",
                                 "violetred1"),
                      aesthetics = c("color",
                                     "fill")) +
  theme(panel.background = element_rect(fill = "lightblue"))
```
